Replicator-mutator and noise-perturbed replicator dynamics

### 2013-10-29 snippets/RMD_nRD.tex
RMD receiver proof

\begin{proof}
  Fix $\Rmixed$ and $\Rstrat = G(\Rmixed)$. The rhs of the consequent
  expands to:
  \begin{align*}
    C(\Rstrat)(\state_x \probbar \messg_y) & = \sum_{\state_j}
    \sum_{i \in \set{k \setbar \Rpure_k(\messg_y) = \state_x}}
    \Rmixed_i \cdot C_{jx} \\
    & = \sum_{\Rpure_i} \sum_{j \in \set{k \setbar \Rpure_i(\messg_y) = \state_j}}
    \Rmixed_i \cdot C_{jx} \\
    & = \sum_{\Rpure_i} \Rmixed_i \cdot C_{\Rpure_i(\messg_y)x} \,.
  \end{align*}
  The rhs expands to:
  \begin{align*}
    G(R^C(\Rmixed))(\state_x \probbar \messg_y) & = \sum_{i}
    \Rmixed_i \cdot \sum_{j \in \set{j \setbar \Rpure_k(\messg_y) =
        \state_x}} 
    \prod_{\messg} C_{\Rstrat_i(\messg)\Rstrat_j(\messg)} \\
    & = \sum_{i}
    \Rmixed_i \cdot ( (C_{\Rpure_i(\messg_1)1} \cdot
      C_{\Rpure_i(\messg_2)1} \cdot \ldots +
      C_{\Rpure_i(\messg_d)1})  \\
      & + \quad (C_{\Rpure_i(\messg_1)1} \cdot
      C_{\Rpure_i(\messg_2)1} \cdot \ldots \cdot
      C_{\Rpure_i(\messg_d)2}) + \ldots  \\
      & + \quad (C_{\Rpure_i(\messg_1)1} \cdot
      C_{\Rpure_i(\messg_2)e} \cdot \ldots \cdot
      C_{\Rpure_i(\messg_d)e}) + \ldots ))
  \end{align*}
  If we assuming without loss of generality that $x=y=1$, then if $d =
  \card{\Messgs}$, we see that:
  \begin{align*}
    \sum_{j \in \set{j \setbar \Rpure_k(\messg_y) = \state_x}}
    \prod_{\messg} C_{\Rstrat_i(\messg)\Rstrat_j(\messg)} = \sum_{i}
    \Rmixed_i \cdot
  \end{align*}
\end{proof}

>>>>

\begin{proof}
  Fix $\Rmixed$ and $\Rstrat = G(\Rmixed)$. The rhs of the consequent
  expands to:
  \begin{align*}
    C(\Rstrat)(\state_x \probbar \messg_y) & = \sum_{\state_j}
    \sum_{i \in \set{k \setbar \Rpure_k(\messg_y) = \state_x}}
    \Rmixed_i \cdot C_{jx} \\
    & = \sum_{\Rpure_i} \sum_{j \in \set{k \setbar \Rpure_i(\messg_y) = \state_j}}
    \Rmixed_i \cdot C_{jx} \\
    & = \sum_{\Rpure_i} \Rmixed_i \cdot C_{\Rpure_i(\messg_y)x} \,.
  \end{align*}
  The rhs expands to:
  \begin{align*}
    G(R^C(\Rmixed))(\state_x \probbar \messg_y) & = \sum_{\Rpure_i}
    \Rmixed_i \cdot \sum_{j \in \set{j \setbar \Rpure_k(\messg_y) =
        \state_x}} 
    \prod_{\messg} C_{\Rpure_i(\messg)\Rpure_j(\messg)}
  \end{align*}
  Without loss of generality, assume that $x=y=1$, and fix
  $\card{M}=d$ and let $e$ be the number of pure receiver
  strategies. Then the last term can be rewritten as:
  \begin{align*}
    & = \sum_{i}
    \Rmixed_i \cdot ( C_{\Rpure_i(\messg_1)1} \cdot
      C_{\Rpure_i(\messg_2)\Rpure_1(\messg_2)} \cdot \ldots \cdot
      C_{\Rpure_i(\messg_d)\Rpure_1(\messg_d)} + \ldots  \\
      & \textcolor{white}{ = \sum_{i}
    \Rmixed_i  (}  +  C_{\Rpure_i(\messg_1)1} \cdot
      C_{\Rpure_i(\messg_2)\Rpure_2(\messg_2)} \cdot \ldots \cdot
      C_{\Rpure_i(\messg_d)\Rpure_2(\messg_d)} + \ldots  \\
      & \textcolor{white}{ = \sum_{i}
    \Rmixed_i  (}  + C_{\Rpure_i(\messg_1)1} \cdot
      C_{\Rpure_i(\messg_2)\Rpure_e(\messg_2)} \cdot \ldots \cdot
      C_{\Rpure_i(\messg_d)\Rpure_e(\messg_d)}) )
  \end{align*}
  Every for every messages $C_{\Rpure_i(\messg_l)}$ is a stochastic
  vector. For $l>1$, all elements of these vectors appear equally
  often. But that means that these cancel out. What remains is:
  \begin{align*}
    & = \sum_{\Rpure_i} \Rmixed_i \cdot C_{\Rpure_i(\messg_y)x} \,.
  \end{align*}
\end{proof}
